Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-08-09 paper.tex
kyle's feedback on goals revision

In this article we
\begin{itemize}
 \item Derive and \add{reproducibly} verify a new Jacobian formulation that greatly increases sparsity\revisedelete{: \texttt{pyJac v2}};
 \item \revisedelete{Enable}\add{Detail the implementation of} cross-platform SIMD\slash SIMT vectorization for CPUs, GPUs, and other accelerators;
 \item Investigate the performance for a wide range chemical kinetic models, specifically looking at speedups due to SIMD\slash SIMT-vectorization as well as relative to a \add{previous version of our analytical chemical kinetic Jacobian code~\cite{Niemeyer:2016aa}}; and finally
 \item Discuss future extensions to this work as well as several promising directions for SIMD\slash SIMT vectorization in reactive-flow simulations.
\end{itemize}
This work builds upon our previous analytical chemical kinetic Jacobian code, \texttt{pyJac}~\cite{Niemeyer:2016aa}\add{, using the new formulation, \texttt{pyJac v2}, to achieve these goals}.
To our knowledge is the first open-source, verified effort that vectorizes the evaluation of chemical-kinetic source terms and Jacobian matrices for any chemical model on a wide selection of platforms.

>>>>

In this article we
\begin{itemize}
 \item Derive and \add{reproducibly} verify a new Jacobian formulation that greatly increases sparsity\revisedelete{: \texttt{pyJac v2}};
 \item \revisedelete{Enable}\add{Detail the implementation of} cross-platform SIMD\slash SIMT vectorization for CPUs, GPUs, and other accelerators;
 \item \revise{Investigate the performance of SIMD\slash SIMT-vectorization for a wide of range chemical kinetic models, and compare with the previous version of our analytical chemical kinetic Jacobian code~\cite{Niemeyer:2016aa}}; and finally}
 \item Discuss future extensions to this work as well as several promising directions for SIMD\slash SIMT vectorization in reactive-flow simulations.
\end{itemize}
This work builds upon our previous analytical chemical kinetic Jacobian code, \texttt{pyJac}~\cite{Niemeyer:2016aa}\add{, using the new formulation, \texttt{pyJac v2}, to achieve these goals}.
To our knowledge is the first open-source, verified effort that vectorizes the evaluation of chemical-kinetic source terms and Jacobian matrices for any chemical model on a wide selection of platforms.
